Stock enhancement undermines community stability

### 2022-02-02 rmd/figures.Rmd
edit: rmd

**Figure 1** Theory and empirical observations agree that stock enhancement destabilizes community dynamics. In A and B, panels and colors distinguish response variables and species groups, respectively. (A) Theoretical predictions. Dots represent individual simulation replicates, and lines and shades are loess curves fitted to simulated data and their 95% confidence intervals. Parameters used in this simulation are: intrinsic growth rate of the enhanced species $r_1=$ `r unique(df0$r1)`, average interspecific competition $\bar{\alpha}=$ `r unique(df0$alpha)`, carrying capacity $K=$ `r unique(df0$k)`, relative fitness of captive-bred individuals $f_R=$ `r unique(df0$phi)`. (B) Empirical evidence. Dots represent observed values in 31 watersheds. Site-level values were averaged in each watershed (geometric mean). Lines are predicted values of regression models, and line types corresponds to posterior probabilities of regression coefficients. See Tables S8-10 for full statistics. (C) Map of sampling sites (black dots) in Hokkaido, Japan. (D) Example of an protected watershed (Okushibetsu). (E) Masu salmon *Oncorhynchus masou masou*. Photo credit: Akira Terui.

>>>>

**Figure 1** Theory and empirical observations agree that stock enhancement destabilizes community dynamics. In A and B, panels and colors distinguish response variables and species groups, respectively. (A) Theoretical predictions. Dots represent individual simulation replicates, and lines and shades are loess curves fitted to simulated data and their 95% confidence intervals. Parameters used in this simulation are: intrinsic growth rate of the enhanced species $r_1=$ `r unique(df0$r1)`, average interspecific competition $\bar{\alpha}=$ `r unique(df0$alpha)`, carrying capacity $K=$ `r unique(df0$k)`, environmental stochasticity $\sigma_{\epsilon}=$ `r unique(df0$sd_env)`, relative fitness of captive-bred individuals $f_R=$ `r unique(df0$phi)`. (B) Empirical evidence. Dots represent observed values in 31 watersheds. Site-level values were averaged in each watershed (geometric mean). Lines are predicted values of regression models, and line types corresponds to posterior probabilities of regression coefficients. See Tables S8-10 for full statistics. (C) Map of sampling sites (black dots) in Hokkaido, Japan. (D) Example of an protected watershed (Okushibetsu). (E) Masu salmon *Oncorhynchus masou masou*. Photo credit: Akira Terui.

### 2022-02-02 rmd/supporting_info.Rmd
edit: rmd

**Time-series data.** We assembled time-series fish data at `r n_distinct(d0$site_id)` sites within `r n_distinct(d0$river)` protected watersheds of Hokkaido Island, Japan. The Hokkaido Research Organization lead a long-term monitoring program at these watersheds, and the data are published as annual reports [@salmonandfreshwaterresearchinstituteAnnualReportMonitoring2021]. The program began in 1963, but an effective, standardized sampling method was implemented since 1999 (two-pass sampling with a combination of electrofishing and cast net). Most data were collected in summer with irregular interannual intervals (1- to 3-year intervals for most cases), and sampling efforts were quantified by sampling area (average: `r op(mean(df_area$area))` $\pm$ `r op(sd(df_area$area))` m^2^). We confined our analysis to the sites that meet the following criteria: (i) the observation span (from the first to the last year of observation) exceeds 10 years, (ii) the number of observation years exceeds five years, and (iii) masu salmon is observed at least twice during the observation period. As a result, we used time-series data at `r n_distinct(df_fish$site_id)` sites within `r n_distinct(df_fish$river)` watersheds from 1999 to 2019. Summed abundance of first and second passes was used in the following analysis. **Table S5** summarizes observed species in these watersheds.

@@

**Environmental data.** At each sampling site, we measured the following environmental variables as potential covariates: upstream watershed area (km^2^; a proxy for stream size), proportional land use in the upstream watershed (forest), local climates (annual mean air temperature [degree Celsius] and cumulative precipitation [mm]), and ocean productivity (Chlorophyll a [unit]). We used MERIT Hydro [@yamazakiMERITHydroHighresolution2019] to delineate upstream watershed polygons for each sampling site. We estimated the proportion of forest land use in each watershed polygon based on land-use data in 2015 from Copernicus Global Land Service (100-m resolution) [@marcelbuchhornCopernicusGlobalLand2020]. Climate data at each sampling site were extracted from CHELSA version 1.2 [@kargerClimatologiesHighResolution2017; @kargerDataClimatologiesHigh2018]. Annual data of ocean productivity (2003-2019) were extracted from OceanColor [@seawifsmissionpageNasaOceanBiology2019] and we calculated the average value within the 30-km radius of each river mouth. We used the following R packages to perform geospatial analysis: *sf* [@pebesmaSimpleFeaturesStandardized2018]*, raster* [@hijmansRasterGeographicData2020]*, exactextractr* [@bastonExactextractrFastExtraction2020]*, stars* [@pebesmaStarsSpatiotemporalArrays2020]*, whitebox* [@lindsayWhiteboxGATCase2016]*.*

@@

```{=tex}
\begin{align}
\gamma_{0,w} &\sim Normal(\mu_{\gamma,w},\sigma_{\gamma}^2)\\
\mu_{\gamma,w} &=\delta_0+\sum_k\delta_k z_{k,w}
\end{align}
```
$\delta_{0}$ is the watershed-specific intercept and $\delta_k (k > 0)$ are the regression coefficients. The watershed-level predictors $z_{k,w}$ include the number of masu salmon released (average of 1999-2019) and ocean productivity (Chlorophyll a). The parameter $\sigma_{\gamma}$ accounts for random variation among watersheds that the watershed-level predictors cannot capture. All predictors were standardized (mean = 0, SD = 1) before the analysis.

>>>>

**Time-series data.** We assembled time-series fish data at `r n_distinct(d0$site_id)` sites within `r n_distinct(d0$river)` protected watersheds of Hokkaido Island, Japan. The Hokkaido Research Organization leads a long-term monitoring program at these watersheds, and the data are published as annual reports [@salmonandfreshwaterresearchinstituteAnnualReportMonitoring2021]. The program began in 1963, but an effective, standardized sampling method has been implemented since 1999 (two-pass sampling with a combination of electrofishing and cast net). Most data were collected in summer with irregular interannual intervals (1- to 3-year intervals for most cases), and sampling efforts were quantified by sampling area (average: `r op(mean(df_area$area))` $\pm$ `r op(sd(df_area$area))` m^2^). We confined our analysis to the sites that meet the following criteria: (i) the observation span (from the first to the last year of observation) exceeds 10 years, (ii) the number of observation years exceeds five years, and (iii) masu salmon is observed at least twice during the observation period. As a result, we used time-series data at `r n_distinct(df_fish$site_id)` sites within `r n_distinct(df_fish$river)` watersheds from 1999 to 2019. Summed abundance of first and second passes was used in the following analysis. **Table S5** summarizes observed species in these watersheds.

@@

**Environmental data.** At each sampling site, we measured the following environmental variables as potential covariates: upstream watershed area (km^2^; a proxy for stream size), proportional land use in the upstream watershed (forest), local climates (annual mean air temperature [degree Celsius] and cumulative precipitation [mm]), and ocean productivity (chlorophyll a [mg m^-3^]). We used MERIT Hydro [@yamazakiMERITHydroHighresolution2019] to delineate upstream watershed polygons for each sampling site. We estimated the proportion of forest land use in each watershed polygon based on land-use data in 2015 from Copernicus Global Land Service (100-m resolution) [@marcelbuchhornCopernicusGlobalLand2020]. Climate data at each sampling site were extracted from CHELSA version 1.2 [@kargerClimatologiesHighResolution2017; @kargerDataClimatologiesHigh2018]. Annual data of ocean productivity (2003-2019) were extracted from OceanColor [@seawifsmissionpageNasaOceanBiology2019] and we calculated the average value within the 30-km radius of each river mouth. We used the following R packages to perform geospatial analysis: *sf* [@pebesmaSimpleFeaturesStandardized2018]*, raster* [@hijmansRasterGeographicData2020]*, exactextractr* [@bastonExactextractrFastExtraction2020]*, stars* [@pebesmaStarsSpatiotemporalArrays2020]*, whitebox* [@lindsayWhiteboxGATCase2016]*.*

@@

```{=tex}
\begin{align}
\gamma_{0,w} &\sim Normal(\mu_{\gamma,w},\sigma_{\gamma}^2)\\
\mu_{\gamma,w} &=\delta_0+\sum_k\delta_k z_{k,w}
\end{align}
```
$\delta_{0}$ is the watershed-specific intercept and $\delta_k (k > 0)$ are the regression coefficients. The watershed-level predictors $z_{k,w}$ include the number of masu salmon released (average of 1999-2019) and ocean productivity (chlorophyll a). The parameter $\sigma_{\gamma}$ accounts for random variation among watersheds that the watershed-level predictors cannot capture. All predictors were standardized (mean = 0, SD = 1) before the analysis.
